---
title: "07_Medium"
author: "Joris Van Meenen"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Setup

## Load modules

```{r}
library(dplyr)
library(ggplot2)
library(ggprism)
library(ggforce)
library(tidyr)
library(scales)
library(rstatix)
library(ggpubr)
library(emmeans)
library(sandwich)
library(zoo)

set.seed(42)
```

## Data to long

```{r}
## Initialise variables
long <- data.frame()
startDate <- as.Date("20250824", format="%Y%m%d")
dir = "D://Documents//Work//Data//Cornea-on-chip//Epithelial barrier//07_Medium//EVOM3//"

## Load and concatenate csv files
csvList = list.files(path = dir, pattern = "*.CSV", full.names = TRUE)

for (csv in csvList) {
  ## Extract resistance values
  df <- read.csv(
    file.path(csv),
    skip = 7,
    header = TRUE,
    stringsAsFactors = FALSE,
    check.names = FALSE
  )
  df <- df[1:8,2:13]
  resistance <- as.vector(t(df))
  resistance <- resistance[resistance > 0]
  df <- data.frame("Resistance (Ω)" = resistance, check.names = FALSE)
  ## Filter out calibration measurements
  df <- df %>% 
    mutate(
      Condition = case_when(
        (row_number() == 1 & `Resistance (Ω)` >= 995 & `Resistance (Ω)` <= 1005) ~ "Calibration resistor",
        (`Resistance (Ω)` >= 30 & `Resistance (Ω)` <= 50) ~ "Measurement medium",
        TRUE ~ "TBD"
      ),
      ## Each medium measurement designates a separate set of measurements
      Measurement = cumsum(Condition == "Measurement medium")
    )
  
  ## Cleanup pre-measurements that test for changes due to media change
  if (max(df$Measurement) > 1) {
    df$Measurement <- ifelse(
      df$Measurement == 1, 
      2, 
      ifelse(
        df$Measurement == 2, 
        1, 
        df$Measurement
      )
    )
  }
  
  ## Cleanup measurements and add conditions
  if (min(df$Measurement) < 1) {
    df[df$Measurement == 0, "Measurement"] <- 1
  }
  df[df$Condition == "TBD", "Condition"] <- rep(c("PBS", "HCE-T", "CnT-PR", "CnT-2D", "CnT-3D"), times = sum(df$Condition == "TBD")/5)
  
  ## Add date and day variables
  name <- basename(csv)
  date <- as.Date(strsplit(name, "_")[[1]][2], format="%Y%m%d")
  dateDiff <- as.double(date - startDate)
  df["Date"] <- rep(date, nrow(df))
  df["Days after seeding"] <- rep(dateDiff, nrow(df))
  
  ## Add plate, row, column and replicate variables
  if (substr(csv, nchar(csv) - 4, nchar(csv)-4) == "1") {
    
    df[df$Measurement == 1, "Plate"] <- c(NA, NA, rep(c(1, 1, 2, 2, 3), each = 10))
    df[df$Measurement == 1, "Row"] <- c(NA, NA, rep(c(1, 2, 3, 4, 1, 2, 3, 4, 2, 3), each = 5))
    df[df$Measurement == 1, "Column"] <- c(NA, NA, rep(c(1, 2, 3, 4, 5), times = 10))
    df[df$Measurement == 1, "Replicate"] <- c(1, 1, rep(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), each = 5))
    if (max(df$Measurement) > 1) {
      df[df$Measurement == 2, "Plate"] <- c(NA, rep(c(1), times = 20))
      df[df$Measurement == 2, "Row"] <- c(NA, rep(c(1, 2, 3, 4), each = 5))
      df[df$Measurement == 2, "Column"] <- c(NA, rep(c(1, 2, 3, 4, 5), times = 4))
      df[df$Measurement == 2, "Replicate"] <- c(1, rep(c(1, 2, 3, 4), each = 5))
    }
    
    PBS <- rep("Before PBS", length(resistance))
    
  } else {
    
    df[df$Measurement == 1, "Plate"] <- c(NA, rep(c(1, 1, 2, 2, 3), each = 10))
    df[df$Measurement == 1, "Row"] <- c(NA, rep(c(1, 2, 3, 4, 1, 2, 3, 4, 2, 3), each = 5))
    df[df$Measurement == 1, "Column"] <- c(NA, rep(c(1, 2, 3, 4, 5), times = 10))
    df[df$Measurement == 1, "Replicate"] <- c(1, rep(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), each = 5))
    if (max(df$Measurement) > 1) {
      df[df$Measurement == 2, "Plate"] <- c(NA, rep(c(1), times = 20))
      df[df$Measurement == 2, "Row"] <- c(NA, rep(c(1, 2, 3, 4), each = 5))
      df[df$Measurement == 2, "Column"] <- c(NA, rep(c(1, 2, 3, 4, 5), times = 4))
      df[df$Measurement == 2, "Replicate"] <- c(1, rep(c(1, 2, 3, 4), each = 5))
    }
    
    PBS <- rep("After incubation", length(resistance))
  }
  
  if (name == "Plate_20250825_2.CSV") {
    PBS <- rep("After PBS", length(resistance))
  }
  df["PBS"] <- PBS
  
  ## Merge all csv files
  long <- dplyr::bind_rows(long, df)
}

## Set to factor to enable statistics bracket placement
long$Condition <- factor(long$Condition, levels = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium"))

long <- long %>%
  mutate(Group = case_when(
    Condition %in% c("Hydrogel control", "Control", "Calibration resistor", "Measurement medium", "Artificial tears") ~ "No cells",
    TRUE ~ "Cells"
  ))

long
```

## Platemap

```{r, fig.height=4, fig.width=12}

dat <- long[long$Measurement == 1 & long$PBS == "Before PBS" & !is.na(long$Plate),]
dat$Plate <- paste0("Plate ", as.character(dat$Plate))
x <- dat$Column
y <- dat$Row

ggplot(data = dat, aes(x = factor(Column), y = reorder(Row, desc(Row)), color = factor(Condition, levels = c("PBS", "HCE-T", "CnT-PR", "CnT-2D", "CnT-3D")))) + 
  geom_point(shape = 16, size = 14) +
  xlab(names(which(sapply(dat, identical, y = x)))) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  facet_wrap(~ Plate) +
  theme_prism() +
  theme(
    axis.line = element_blank(),
    axis.ticks = element_blank()
  ) +
  theme(aspect.ratio = 0.713)
```

# Resistance

## Visualise data before PBS

```{r}
dat <- long[long$Measurement == 1 & long$PBS == "Before PBS",]

control_conditions <- c("Calibration resistor", "Measurement medium")
interesting_conditions <- setdiff(unique(dat$Condition), control_conditions)
dat_background <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_facet = Condition) %>%
  crossing(Condition_display = interesting_conditions) %>%
  filter(Condition_facet != Condition_display)
dat_interesting <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_display = Condition)
dat_control <- dat %>%
  filter(Condition %in% control_conditions) %>%
  crossing(Condition_display = interesting_conditions)

ggplot(data = dat, aes(x = `Days after seeding`, y = `Resistance (Ω)`, color = Condition)) + 
  geom_line(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_line(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_point(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_line(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_vline(xintercept = 8, linetype="dashed") +
  annotate("text", x=8, y=200, label="Start", hjust = 1.2) +
  geom_vline(xintercept = 15, linetype="dashed") +
  annotate("text", x=15, y=200, label="Viability", hjust = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(limits = c(0, 1000), expand = c(0, 0), oob = scales::oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 20), expand = c(0, 0), guide = guide_prism_minor(), minor_breaks = seq(0, 20, 1)) +
  facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS")), scales = "free") +
  scale_color_manual(
    breaks = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "CnT-PR" = "#DB8E00", "CnT-2D" = "#AEA200", "CnT-3D" = "#64B200", "PBS" = "#00BD5C", "Calibration resistor" = "#00C1A7", "Measurement medium" = "#00BADE")) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(panel.spacing.x = unit(1.5, "lines"), legend.key.spacing.y = unit(0.5, "lines"))
```

## Visualise data after PBS

```{r}
dat <- long[long$Measurement == 1 & long$PBS == "After incubation",]

control_conditions <- c("Calibration resistor", "Measurement medium")
interesting_conditions <- setdiff(unique(dat$Condition), control_conditions)
dat_background <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_facet = Condition) %>%
  crossing(Condition_display = interesting_conditions) %>%
  filter(Condition_facet != Condition_display)
dat_interesting <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_display = Condition)
dat_control <- dat %>%
  filter(Condition %in% control_conditions) %>%
  crossing(Condition_display = interesting_conditions)

ggplot(data = dat, aes(x = `Days after seeding`, y = `Resistance (Ω)`, color = Condition)) + 
  geom_line(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_line(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_point(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_line(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_vline(xintercept = 8, linetype="dashed") +
  annotate("text", x=8, y=200, label="Start", hjust = 1.2) +
  geom_vline(xintercept = 15, linetype="dashed") +
  annotate("text", x=15, y=200, label="Viability", hjust = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(limits = c(0, 1000), expand = c(0, 0), oob = scales::oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 20), expand = c(0, 0), guide = guide_prism_minor(), minor_breaks = seq(0, 20, 1)) +
  facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS")), scales = "free") +
  scale_color_manual(
    breaks = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "CnT-PR" = "#DB8E00", "CnT-2D" = "#AEA200", "CnT-3D" = "#64B200", "PBS" = "#00BD5C", "Calibration resistor" = "#00C1A7", "Measurement medium" = "#00BADE")) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(panel.spacing.x = unit(1.5, "lines"), legend.key.spacing.y = unit(0.5, "lines"))
```

## Visualisation: Medium change

```{r}

dat <- long %>%
  filter(!is.na(Plate)) %>%
  filter(PBS == "Before PBS") %>%
  filter(Condition != "Control") %>%
  group_by(`Days after seeding`) %>%
  filter(n_distinct(Measurement) == 2)

lapply(split(dat, dat$`Days after seeding`), function(z) {
  ggplot(data = z, aes(x = reorder(Measurement, desc(Measurement)), y = `Resistance (Ω)`, color = Condition, group = interaction(Condition, Measurement))) + 
    xlab("Measurement") +
    scale_x_discrete(label = c("Before", "After")) +
    geom_violin(width = 0.5, scale = "width", position = position_dodge(width = 0.8), alpha = 0.2, colour = "black", linewidth = 1) +
    geom_sina(size = 4, maxwidth = 0.5, position = position_dodge(width = 0.8), scale = FALSE, alpha = 0.4, stroke = 0) +
    theme_prism(base_size = 28) +
    theme(axis.title.x = element_blank())
})
```

## Metrics: CV

```{r}
dat <- long[long$Measurement == 1 & long$PBS == "Before PBS" & !is.na(long$Plate),]
cv <- dat %>%
  filter(!is.na(Plate)) %>%
  group_by(Condition, Replicate) %>%
  arrange(`Days after seeding`) %>%
  mutate(CV = rollapply(
    data = `Resistance (Ω)`,
    width = 3,
    FUN = function(x) {
      sd(x)/mean(x) * 100
    },
    align = "right",
    fill = NA
  )) %>%
  ungroup() %>% 
  mutate(`CV <= 15%` = case_when(
    CV <= 15 ~ TRUE,
    CV > 15 ~ FALSE,
    TRUE ~ NA
  ))
```

## Visualisation: CV

```{r}
dat <- cv
x <- factor(dat$Replicate)
y <- reorder(dat$`Days after seeding`, desc(dat$`Days after seeding`))

ggplot(data = dat, aes(x = x, y = y, color = `CV <= 15%`)) + 
  geom_point(shape = 16, size = 8) +
  xlab("Replicate") +
  ylab("Days after seeding") +
  facet_wrap(~ Condition) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(axis.line = element_blank(), axis.ticks = element_blank(), panel.spacing.x = unit(1.5, "lines"), legend.title = element_text(), legend.title.position = "top")
```

# Metrics: nTEER

## Calculate (n)TEER

Incubation in PBS at every timepoint, empty control estimated from controls in other experiments

```{r}
#control_min <- min(experiment1_control$`Resistance (Ω)`, experiment3_control$`Resistance (Ω)`, experiment4_control$`Resistance (Ω)`)
control_min <- 222
#control_mean <- mean(c(experiment1_control$`Resistance (Ω)`, experiment3_control$`Resistance (Ω)`, experiment4_control$`Resistance (Ω)`))
control_mean <- 266.909385113269
#control_max <- max(experiment1_control$`Resistance (Ω)`, experiment3_control$`Resistance (Ω)`, experiment4_control$`Resistance (Ω)`)
control_max <- 290

nTEER <- long %>%
  filter(!is.na(Plate)) %>%
  group_by(Date, `Days after seeding`, Condition, Replicate) %>%
  reframe(
    `Max TEER (Ω*cm²)` = (`Resistance (Ω)`[PBS == "Before PBS"] - control_min) * 0.3359273609,
    `TEER (Ω*cm²)` = (`Resistance (Ω)`[PBS == "Before PBS"] - control_mean) * 0.3359273609,
    `Min TEER (Ω*cm²)` = (`Resistance (Ω)`[PBS == "Before PBS"] - control_max) * 0.3359273609,
    `nTEER (Ω*cm²)` = (`Resistance (Ω)`[PBS == "Before PBS"] - `Resistance (Ω)`[PBS == "After incubation"]) * 0.3359273609,
  )

```

## Visualise TEER

```{r}
dat <- nTEER

control_conditions <- c("Calibration resistor", "Measurement medium")
interesting_conditions <- setdiff(unique(dat$Condition), control_conditions)
dat_background <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_facet = Condition) %>%
  crossing(Condition_display = interesting_conditions) %>%
  filter(Condition_facet != Condition_display)
dat_interesting <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_display = Condition)
dat_control <- dat %>%
  filter(Condition %in% control_conditions) %>%
  crossing(Condition_display = interesting_conditions)

ggplot(data = dat, aes(x = `Days after seeding`, y = `Max TEER (Ω*cm²)`, color = Condition)) + 
  geom_line(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_line(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_point(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_line(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_vline(xintercept = 8, linetype="dashed") +
  annotate("text", x=8, y=-25, label="Start", hjust = 1.2) +
  geom_vline(xintercept = 15, linetype="dashed") +
  annotate("text", x=15, y=-25, label="Viability", hjust = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(limits = c(-50, 150), expand = c(0, 0), oob = scales::oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 20), expand = c(0, 0), guide = guide_prism_minor(), minor_breaks = seq(0, 20, 1)) +
  facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium")), scales = "free") +
  scale_color_manual(
    breaks = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "CnT-PR" = "#DB8E00", "CnT-2D" = "#AEA200", "CnT-3D" = "#64B200", "PBS" = "#00BD5C", "Calibration resistor" = "#00C1A7", "Measurement medium" = "#00BADE")) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(panel.spacing.x = unit(1.5, "lines"), legend.key.spacing.y = unit(0.5, "lines"))
```

## Visualise nTEER

```{r}
dat <- nTEER

control_conditions <- c("Calibration resistor", "Measurement medium")
interesting_conditions <- setdiff(unique(dat$Condition), control_conditions)
dat_background <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_facet = Condition) %>%
  crossing(Condition_display = interesting_conditions) %>%
  filter(Condition_facet != Condition_display)
dat_interesting <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_display = Condition)
dat_control <- dat %>%
  filter(Condition %in% control_conditions) %>%
  crossing(Condition_display = interesting_conditions)

ggplot(data = dat, aes(x = `Days after seeding`, y = `nTEER (Ω*cm²)`, color = Condition)) + 
  geom_line(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_line(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_point(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_line(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_vline(xintercept = 8, linetype="dashed") +
  annotate("text", x=8, y=-25, label="Start", hjust = 1.2) +
    geom_vline(xintercept = 15, linetype="dashed") +
  annotate("text", x=15, y=-25, label="Viability", hjust = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(limits = c(-50, 150), expand = c(0, 0), oob = scales::oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 20), expand = c(0, 0), guide = guide_prism_minor(), minor_breaks = seq(0, 20, 1)) +
  facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium")), scales = "free") +
  scale_color_manual(
    breaks = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "CnT-PR" = "#DB8E00", "CnT-2D" = "#AEA200", "CnT-3D" = "#64B200", "PBS" = "#00BD5C", "Calibration resistor" = "#00C1A7", "Measurement medium" = "#00BADE")) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(panel.spacing.x = unit(1.5, "lines"), legend.key.spacing.y = unit(0.5, "lines"))

```

# Before vs after

## Statistics: by condition

```{r}
dat <- droplevels(nTEER[nTEER$`Days after seeding` == 8 | nTEER$`Days after seeding` == 15,])
dat$`Days after seeding` <- factor(dat$`Days after seeding`, levels = c(8, 15), labels = c("Before", "After"))
renamed_dat <- dat %>%
  rename(nTEER = `nTEER (Ω*cm²)`) %>%
  rename(Time = `Days after seeding`)

model <- lm(nTEER ~ Time * Condition, data = renamed_dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`nTEER (Ω*cm²)`",
         facet.by = c("Days after seeding", "Condition"),
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
shapiro_individual <- renamed_dat %>%
  group_by(Time, Condition) %>%
  shapiro_test(nTEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`nTEER (Ω*cm²)` ~ `Days after seeding` * Condition)
dat_summary <- dat %>%
  group_by(`Days after seeding`, Condition) %>%
  get_summary_stats(`nTEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 3, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_Resistance <- emmeans(model, ~ Time * Condition, vcov. = vcovHC3)
pairs(emm_Resistance, by = "Condition", adjust = "bonferroni")
stat_Resistance <- summary(pairs(emm_Resistance, by = "Condition", adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_Resistance_pos <- stat_Resistance %>%
  add_xy_position(
    x = "Time",
    data = renamed_dat,
    formula = nTEER ~ Time,
  ) %>%
  mutate(
    xmin = match(group1, levels(renamed_dat$Time)),
    xmax = match(group2, levels(renamed_dat$Time)),
  ) %>% 
  group_by(Condition) %>%
  mutate(
    y.position = max(renamed_dat$nTEER[renamed_dat$Condition == unique(Condition)]) + (row_number() * max(renamed_dat$nTEER[renamed_dat$Condition == unique(Condition)])/5)
    ) %>%
  ungroup()
```

## Visualisation: by condition

```{r}
dat <- droplevels(nTEER[nTEER$`Days after seeding` == 8 | nTEER$`Days after seeding` == 15,])
dat$`Days after seeding` <- factor(dat$`Days after seeding`, levels = c(8, 15), labels = c("Before", "After"))
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = `Days after seeding`, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 4, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  coord_cartesian(clip = "off") +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(-50, 150), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  stat_pvalue_manual(
    stat_Resistance_pos,
    label = "p.adj.signif",
    tip.length = 0.025,
    size = 7.76,
    linewidth = 1,
  ) +
  geom_hline(yintercept = 0, linetype="dashed") +
  scale_color_manual(
    breaks = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Reservoir", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "CnT-PR" = "#DB8E00", "CnT-2D" = "#AEA200", "CnT-3D" = "#64B200", "PBS" = "#00BD5C", "Reservoir" = "#00C1A7", "Measurement medium" = "#00BADE")) +
    facet_wrap(~ factor(Condition, levels = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS")), scales = "free") +
    theme_prism(base_size = 28) +
    theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"))


```

## Statistics: by time

```{r}
dat <- droplevels(nTEER[nTEER$`Days after seeding` == 8 | nTEER$`Days after seeding` == 15,])
dat$`Days after seeding` <- factor(dat$`Days after seeding`, levels = c(8, 15), labels = c("Before", "After"))
renamed_dat <- dat %>%
  rename(nTEER = `nTEER (Ω*cm²)`) %>%
  rename(Time = `Days after seeding`)

model <- lm(nTEER ~ Time * Condition, data = renamed_dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`nTEER (Ω*cm²)`",
         facet.by = c("Days after seeding", "Condition"),
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
shapiro_individual <- renamed_dat %>%
  group_by(Time, Condition) %>%
  shapiro_test(nTEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`nTEER (Ω*cm²)` ~ `Days after seeding` * Condition)
dat_summary <- dat %>%
  group_by(`Days after seeding`, Condition) %>%
  get_summary_stats(`nTEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 3, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_Resistance <- emmeans(model, ~ Time * Condition, vcov. = vcovHC3)
pairs(emm_Resistance, by = "Time", adjust = "bonferroni")
stat_Resistance <- summary(pairs(emm_Resistance, by = "Time", adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_Resistance_pos <- stat_Resistance %>%
  add_xy_position(
    x = "Condition",
    data = renamed_dat,
    formula = nTEER ~ Condition,
  ) %>%
  mutate(
    xmin = match(group1, levels(renamed_dat$Condition)),
    xmax = match(group2, levels(renamed_dat$Condition)),
  ) %>% 
  group_by(Time) %>%
  mutate(
    y.position = max(renamed_dat$nTEER[renamed_dat$Time == unique(Time)]) + (row_number() * 10)
    ) %>%
  ungroup() %>%
  rename(`Days after seeding` = Time)
```

## Visualisation: by time

```{r}
dat <- droplevels(nTEER[nTEER$`Days after seeding` == 8 | nTEER$`Days after seeding` == 15,])
dat$`Days after seeding` <- factor(dat$`Days after seeding`, levels = c(8, 15), labels = c("Before", "After"))
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = Condition, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 4, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  coord_cartesian(clip = "off") +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(-50, 200), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  stat_pvalue_manual(
    stat_Resistance_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  geom_hline(yintercept = 0, linetype="dashed") +
  scale_color_manual(
    breaks = c("HCE-T", "CnT-PR", "CnT-2D", "CnT-3D", "PBS", "Reservoir", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "CnT-PR" = "#DB8E00", "CnT-2D" = "#AEA200", "CnT-3D" = "#64B200", "PBS" = "#00BD5C", "Reservoir" = "#00C1A7", "Measurement medium" = "#00BADE")) +
    facet_wrap(~ factor(`Days after seeding`, levels = c("Before", "After")), scales = "free") +
    theme_prism(base_size = 28) +
    theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"))


```

# Meta

## Measurement medium

### Data

```{r}
experiment2_medium <- long[long$PBS == "Before PBS" & long$Condition == "Measurement medium",]

```

### Visualisation

```{r}
dat <- experiment2_medium
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())
```

## Controls

Not included in experiment

## HCE-T

### Data

Limiting non-HCE-T data points to 8 days after seeding to avoid any influence of the induced conditions


```{r}
experiment2_hcet_resistance <- long[long$Group == "Cells" & long$`Days after seeding` <= 8 & long$PBS == "Before PBS" | long$Condition == "HCE-T" & long$PBS == "Before PBS",]
experiment2_hcet_nTEER <- nTEER[nTEER$Condition == "HCE-T",]
```

### Visualisation

```{r}
dat <- experiment2_hcet_resistance
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment2_hcet_nTEER
x <- rep("Experiment 1", length(dat$`TEER (Ω*cm²) min`))
y <- dat$`TEER (Ω*cm²) min`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment2_hcet_nTEER
x <- rep("Experiment 1", length(dat$`TEER (Ω*cm²)`))
y <- dat$`TEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment2_hcet_nTEER
x <- rep("Experiment 1", length(dat$`TEER (Ω*cm²) max`))
y <- dat$`TEER (Ω*cm²) max`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment2_hcet_nTEER
x <- rep("Experiment 1", length(dat$`nTEER (Ω*cm²)`))
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

```
