---
title: "Supplements"
author: "Joris Van Meenen"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Setup

### Load modules

```{r}
library(dplyr)
library(ggplot2)
library(ggprism)
library(ggforce)
library(tidyr)
library(scales)
library(rstatix)
library(ggpubr)
library(emmeans)
library(sandwich)
library(zoo)

set.seed(42)

```

### Data to long

```{r}

## Initialise variables
long <- data.frame()
startDate <- as.Date("20251103", format="%Y%m%d")
dir = "D://Documents//Work//Data//Cornea-on-chip//Epithelial barrier//08_Supplements//EVOM3//"
controlList <- c("Plate_20251119_1.CSV", "Plate_20251119_2.CSV", "Plate_20251121_1.CSV", "Plate_20251124_1.CSV")

## Load and concatenate csv files
csvList = list.files(path = dir, pattern = "*.CSV", full.names = TRUE)

for (csv in csvList) {
  ## Extract resistance values
  df <- read.csv(
    file.path(csv),
    skip = 7,
    header = TRUE,
    stringsAsFactors = FALSE,
    check.names = FALSE
  )
  df <- df[1:8,2:13]
  resistance <- as.vector(t(df))
  resistance <- resistance[resistance > 0]
  df <- data.frame("Resistance (Ω)" = resistance, check.names = FALSE)
  ## Filter out calibration measurements
  df <- df %>% 
    mutate(
      Condition = case_when(
        (row_number() == 1 & `Resistance (Ω)` >= 995 & `Resistance (Ω)` <= 1005) ~ "Calibration resistor",
        (`Resistance (Ω)` >= 30 & `Resistance (Ω)` <= 50) ~ "Measurement medium",
        (`Resistance (Ω)` >= 200 & `Resistance (Ω)` <= 300) ~ "Control",
        TRUE ~ "TBD"
      ),
      ## Each medium measurement designates a separate set of measurements
      Measurement = cumsum(Condition == "Measurement medium")
    )
  
  ## Cleanup pre-measurements that test for changes due to media change
  if (max(df$Measurement) > 1) {
    df$Measurement <- ifelse(
      df$Measurement == 1, 
      2, 
      ifelse(
        df$Measurement == 2, 
        1, 
        df$Measurement
      )
    )
  }
  
  ## Cleanup measurements and add conditions
  if (min(df$Measurement) < 1) {
    df[df$Measurement == 0, "Measurement"] <- 1
  }
  df[df$Condition == "TBD", "Condition"] <- rep(c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1"), times = sum(df$Condition == "TBD")/6)
  
  ## Add date and day variables
  name <- basename(csv)
  date <- as.Date(strsplit(name, "_")[[1]][2], format="%Y%m%d")
  dateDiff <- as.double(date - startDate)
  df["Date"] <- rep(date, nrow(df))
  df["Days after seeding"] <- rep(dateDiff, nrow(df))
  
  ## Add plate, row, column and replicate variables
  if (name %in% controlList) {
    
    if (name == "Plate_20251119_2.CSV") {
      
      df[df$Measurement == 1, "Plate"] <- c(NA, rep(3, 9), rep(c(1, 1, 2, 2, 3), each = 12))
      df[df$Measurement == 1, "Row"] <- c(NA, rep(1, 5), rep(4, 4), rep(c(1, 2, 3, 4, 1, 2, 3, 4, 2, 3), each = 6))
      df[df$Measurement == 1, "Column"] <- c(NA, 1:5, 1:4, rep(c(1, 2, 3, 4, 5, 6), times = 10))
      df[df$Measurement == 1, "Replicate"] <- c(1, 1:9, rep(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), each = 6))
      
    } else {
      
      df[df$Measurement == 1, "Plate"] <- c(NA, NA, rep(3, 9), rep(c(1, 1, 2, 2, 3), each = 12))
      df[df$Measurement == 1, "Row"] <- c(NA, NA, rep(1, 5), rep(4, 4), rep(c(1, 2, 3, 4, 1, 2, 3, 4, 2, 3), each = 6))
      df[df$Measurement == 1, "Column"] <- c(NA, NA, 1:5, 1:4, rep(c(1, 2, 3, 4, 5, 6), times = 10))
      df[df$Measurement == 1, "Replicate"] <- c(1, 1, 1:9, rep(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), each = 6))
      
      if (max(df$Measurement) > 1) {
        
        df[df$Measurement == 2, "Plate"] <- c(NA, rep(c(1), times = 24))
        df[df$Measurement == 2, "Row"] <- c(NA, rep(c(1, 2, 3, 4), each = 6))
        df[df$Measurement == 2, "Column"] <- c(NA, rep(c(1, 2, 3, 4, 5, 6), times = 4))
        df[df$Measurement == 2, "Replicate"] <- c(1, rep(c(1, 2, 3, 4), each = 6))
      }
    }
    
  } else{
  
    df[df$Measurement == 1, "Plate"] <- c(NA, NA, rep(c(1, 1, 2, 2, 3), each = 12))
    df[df$Measurement == 1, "Row"] <- c(NA, NA, rep(c(1, 2, 3, 4, 1, 2, 3, 4, 2, 3), each = 6))
    df[df$Measurement == 1, "Column"] <- c(NA, NA, rep(c(1, 2, 3, 4, 5, 6), times = 10))
    df[df$Measurement == 1, "Replicate"] <- c(1, 1, rep(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), each = 6))
    if (max(df$Measurement) > 1) {
      df[df$Measurement == 2, "Plate"] <- c(NA, rep(c(1), times = 24))
      df[df$Measurement == 2, "Row"] <- c(NA, rep(c(1, 2, 3, 4), each = 6))
      df[df$Measurement == 2, "Column"] <- c(NA, rep(c(1, 2, 3, 4, 5, 6), times = 4))
      df[df$Measurement == 2, "Replicate"] <- c(1, rep(c(1, 2, 3, 4), each = 6))
    }
  }
  
  if (name == "Plate_20251119_2.CSV") {
    PBS <- rep("After PBS", length(resistance))
  } else {
    PBS <- rep("Before PBS", length(resistance))
  }
  df["PBS"] <- PBS
  
  ## Merge all csv files
  long <- dplyr::bind_rows(long, df)
}

long

## Set to factor to enable statistics bracket placement
long$Condition <- factor(long$Condition, levels = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1", "Control", "Calibration resistor", "Measurement medium"))

long <- long %>%
  mutate(Group = case_when(
    Condition %in% c("Hydrogel control", "Control", "Calibration resistor", "Measurement medium", "Artificial tears") ~ "No cells",
    TRUE ~ "Cells"
  ))
```

### Platemap

```{r, fig.height=4, fig.width=12}

dat <- long[long$Measurement == 1 & long$PBS == "Before PBS" & !is.na(long$Plate) & long$Condition != "Control",]
dat$Plate <- paste0("Plate ", as.character(dat$Plate))
x <- dat$Column
y <- dat$Row

ggplot(data = dat, aes(x = factor(Column), y = reorder(Row, desc(Row)), color = factor(Condition, levels = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1")))) + 
  geom_point(shape = 16, size = 14) +
  xlab(names(which(sapply(dat, identical, y = x)))) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  facet_wrap(~ Plate) +
  theme_prism() +
  theme(
    axis.line = element_blank(),
    axis.ticks = element_blank()
  ) +
  theme(aspect.ratio = 0.713)
```

# Resistance

### Visualisation

As expected, after about a week of culture, the tissues reach a resistance value that seems stable. However, unexpectedly at 16 days, all values increase followed by the typical decline seen in previous experiments. This is again a demonstration of the importance of "living" controls as the resistance values always fluctuate in a way that is currently beyond my comprehension while empty control insert values remain stable, not accounting for those fluctuations. What is also remarkable is the increased resistance values at day 2 and the general increased resistance over previous experiments. The initial increased resistance could be due to accidentally seeding a higher number of cells, which can be seen in the seeding density experiment causes a drop of resistance until the gradual decay phase. The general increased resistance could be due to passage number and is another example as to why TEER measurements cannot be interpreted at face value.

```{r}
dat <- long[long$Measurement == 1 & long$PBS == "Before PBS" & long$`Days after seeding` <= 16,]

control_conditions <- c("Calibration resistor", "Measurement medium", "Control")
interesting_conditions <- setdiff(unique(dat$Condition), control_conditions)
dat_background <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_facet = Condition) %>%
  crossing(Condition_display = interesting_conditions) %>%
  filter(Condition_facet != Condition_display)
dat_interesting <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_display = Condition)
dat_control <- dat %>%
  filter(Condition %in% control_conditions) %>%
  crossing(Condition_display = interesting_conditions)

ggplot(data = dat, aes(x = `Days after seeding`, y = `Resistance (Ω)`, color = Condition)) + 
  geom_line(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_control,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_line(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_point(data = dat_background,
            aes(group = interaction(Condition_facet, Replicate)),
            color = "grey") +
  geom_line(data = dat_interesting,
		        aes(group = interaction(Condition, Replicate))
            ) +
  geom_point(data = dat_interesting,
            aes(group = interaction(Condition, Replicate))
            ) +
  geom_vline(xintercept = 9, linetype="dashed") +
  annotate("text", x=9, y=350, label="Start", hjust = 1.2) +
  geom_vline(xintercept = 16, linetype="dashed") +
  annotate("text", x = 16, y = 350, label = "Diffusion", hjust = 1.1) +
  scale_y_continuous(limits = c(0, 1200), expand = c(0, 0), oob = scales::oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 18), expand = c(0, 0), guide = guide_prism_minor(), minor_breaks = seq(0, 18, 1)) +
  scale_color_manual(
    breaks = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1", "Control", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "Calcium" = "#DB8E00", "GSK" = "#AEA200", "SP" = "#64B200", "SP+IGF1" = "#00BD5C", "IGF1" = "#00C1A7", "Control" = "#00BADE", "Calibration resistor" = "#00A6FF", "Measurement medium" = "#B385FF")) +
  facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1")), scales = "free") +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(panel.spacing.x = unit(1.5, "lines"), legend.key.spacing.y = unit(0.5, "lines"))
```

### Check edge effects after medium change

No obvious edge effects observed except maybe for A1 and B1 of plate 1.

```{r, fig.height=4, fig.width=12}
dat <- long[long$Measurement == 1 & long$PBS == "Before PBS" & !is.na(long$Plate),]
dat$Plate <- paste0("Plate ", as.character(dat$Plate))
x <- dat$Column
y <- dat$Row

lapply(split(dat, dat$Day), function(z) {
  ggplot(data = z, aes(x = factor(Column), y = reorder(Row, desc(Row)), color = `Resistance (Ω)`)) + 
    geom_point(shape = 16, size = 15) +
    scale_fill_continuous(limits = c(min(z$`Resistance (Ω)`[z$`Resistance (Ω)` > 300]), max(z$`Resistance (Ω)`))) +
    xlab(names(which(sapply(dat, identical, y = x)))) +
    ylab(names(which(sapply(dat, identical, y = y)))) +
    facet_wrap(~ Plate) +
    theme_prism() +
    theme(
      axis.line = element_blank(),
      axis.ticks = element_blank()
    ) +
    theme(aspect.ratio = 0.713)
})
```

### Check edge effects before media change

```{r}
dat <- long[long$Measurement == 2 & long$PBS == "Before PBS" & !is.na(long$Plate),]
x <- dat$Column
y <- dat$Row

lapply(split(dat, dat$Day), function(z) {
  ggplot(data = z) + 
    geom_tile(aes(x = factor(Column), y = reorder(Row, desc(Row)), fill = `Resistance (Ω)`)) +
    scale_fill_continuous(limits = c(min(z$`Resistance (Ω)`[z$`Resistance (Ω)` > 300]), max(z$`Resistance (Ω)`))) +
    xlab(names(which(sapply(dat, identical, y = x)))) +
    ylab(names(which(sapply(dat, identical, y = y)))) +
    facet_wrap(~ Plate) +
    theme_prism() +
    theme(aspect.ratio = 0.713)
})
```

## Metrics: CV

Plateau period is from Day 9 to day 14 with a new plateau period starting at day 21.

```{r}
dat <- long[long$Measurement == 1 & long$PBS == "Before PBS" & !is.na(long$Plate),]
cv <- dat %>%
  filter(!is.na(Plate)) %>%
  group_by(Condition, Replicate) %>%
  arrange(`Days after seeding`) %>%
  mutate(CV = rollapply(
    data = `Resistance (Ω)`,
    width = 3,
    FUN = function(x) {
      sd(x)/mean(x) * 100
    },
    align = "right",
    fill = NA
  )) %>%
  ungroup() %>% 
  mutate(`CV <= 15%` = case_when(
    CV <= 15 ~ TRUE,
    CV > 15 ~ FALSE,
    TRUE ~ NA
  ))
```

## Visualisation: CV

```{r}
dat <- cv[cv$Condition != "Control",]
x <- factor(dat$Replicate)
y <- reorder(dat$`Days after seeding`, desc(dat$`Days after seeding`))

ggplot(data = dat, aes(x = x, y = y, color = `CV <= 15%`)) + 
  geom_point(shape = 16, size = 8) +
  xlab("Replicate") +
  ylab("Days after seeding") +
  facet_wrap(~ Condition) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(axis.line = element_blank(), axis.ticks = element_blank(), panel.spacing.x = unit(1.5, "lines"), legend.title = element_text(), legend.title.position = "top")
```

## Check effect medium change

Changing medium has an effect, but to me it does not seem to be masking a significant effect of the conditions

```{r}
dat <- long %>%
  filter(!is.na(Plate)) %>%
  filter(PBS == "Before PBS") %>%
  filter(Condition != "Control") %>%
  group_by(`Days after seeding`) %>%
  filter(n_distinct(Measurement) == 2)

dat$`Days after seeding` <- paste0("Day ", dat$`Days after seeding`)

ggplot(data = dat, aes(x = reorder(Measurement, desc(Measurement)), y = `Resistance (Ω)`, color = Condition, group = interaction(Condition, Measurement))) + 
    xlab("Measurement") +
    scale_x_discrete(label = c("Before", "After")) +
    geom_violin(width = 0.5, scale = "width", position = position_dodge(width = 0.8), alpha = 0.2, colour = "black", linewidth = 1) +
    geom_sina(size = 4, maxwidth = 0.5, position = position_dodge(width = 0.8), scale = FALSE, alpha = 0.4, stroke = 0) +
    facet_wrap(~ `Days after seeding`) +
    theme_prism(base_size = 28) +
    theme(axis.title.x = element_blank())


```

### Check effect PBS

```{r}
dat <- long %>%
  group_by(`Days after seeding`) %>%
  filter(n_distinct(PBS) == 2) %>%
  filter(Measurement == 1) 

ggplot(data = dat) + 
  xlab("") +
  geom_line(aes(x = reorder(PBS, desc(PBS)), y = `Resistance (Ω)`, color = Condition, group = interaction(Condition, Replicate))) + 
  theme_prism() +
  theme(aspect.ratio = 0.713)
```

# nTEER endpoint

## Metrics: nTEER

Control and incubation in PBS only at day 16 after cell seeding

```{r}
control <- mean(long[long$Measurement == 1 & long$`Days after seeding` == 16 & long$Condition == "Control" & long$PBS == "After PBS",]$`Resistance (Ω)`)

nTEER <- long[long$Measurement == 1 & long$`Days after seeding` == 16,] %>%
  filter(!is.na(Plate)) %>%
  group_by(Date, `Days after seeding`, Condition, Replicate) %>%
  reframe(
    `TEER (Ω*cm²)` = (`Resistance (Ω)`[PBS == "Before PBS"] - control) * 0.3359273609,
    `nTEER (Ω*cm²)` = (`Resistance (Ω)`[PBS == "Before PBS"] - `Resistance (Ω)`[PBS == "After PBS"]) * 0.3359273609,
  )
```

## Statistics

```{r}
dat <- nTEER[nTEER$Condition != "Control",]
renamed_dat <- dat %>%
  rename(nTEER = `nTEER (Ω*cm²)`)

model <- lm(`nTEER (Ω*cm²)` ~ Condition, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`nTEER (Ω*cm²)`",
         facet.by = "Condition",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Condition) %>%
  shapiro_test(nTEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`nTEER (Ω*cm²)` ~ Condition)
dat_summary <- dat %>%
  group_by(Condition) %>%
  get_summary_stats(`nTEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_cell <- emmeans(model, ~ Condition, vcov. = vcovHC3)
pairs(emm_cell, adjust = "bonferroni")
stat_cell <- summary(pairs(emm_cell, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_cell_pos <- stat_cell %>%
  add_xy_position(
    x = "Condition",
    data = dat,
    formula = `nTEER (Ω*cm²)` ~ Condition,
  ) %>%
  mutate(y.position = 210 + (row_number() * 25)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Condition))),
    xmax = match(group2, levels(droplevels(dat$Condition))),
  )
```

## Visualisation

```{r}
dat <- nTEER[nTEER$Condition != "Control",]
x <- dat$Condition
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  coord_cartesian(clip = "off") +
  stat_summary(geom = "point", fun = "mean", size = 2, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(-50, 650), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  stat_pvalue_manual(
    stat_cell_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  geom_hline(yintercept = 0, linetype="dashed") +
  scale_color_manual(
    breaks = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1", "Control", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "Calcium" = "#DB8E00", "GSK" = "#AEA200", "SP" = "#64B200", "SP+IGF1" = "#00BD5C", "IGF1" = "#00C1A7", "Control" = "#00BADE", "Calibration resistor" = "#00A6FF", "Measurement medium" = "#B385FF")) +
  theme_prism(base_size = 28) +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())
```

# Meta

## Measurement medium

### Data

```{r}
experiment3_medium <- long[long$PBS == "Before PBS" & long$Condition == "Measurement medium",]

```

### Visualisation

```{r}
dat <- experiment3_medium
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())
```

## Controls

### Data

```{r}
experiment3_control <- long[long$PBS == "Before PBS" & long$Condition == "Control",]
```

### Visualisation

```{r}
dat <- experiment3_control
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(200, 400), expand = c(0, 0)) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

```

## HCE-T

### Data

Limiting non-HCE-T data points to 9 days after seeding to avoid any influence of the induced conditions Limiting data points to 16 days after seeding to avoid any influence of the diffusion assay on day 16

```{r}
experiment3_hcet_resistance <- long[long$Group == "Cells" & long$`Days after seeding` <= 9 & long$PBS == "Before PBS" | long$Condition == "HCE-T" & long$PBS == "Before PBS" & long$`Days after seeding` <= 16,]
experiment3_hcet_nTEER <- nTEER[nTEER$Condition == "HCE-T",]
```

### Visualisation

```{r}
dat <- experiment3_hcet_resistance
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment3_hcet_nTEER
x <- rep("Experiment 1", length(dat$`TEER (Ω*cm²)`))
y <- dat$`TEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment3_hcet_nTEER
x <- rep("Experiment 1", length(dat$`nTEER (Ω*cm²)`))
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

```
