---
title: "08_Supplements-FITC-Dextran"
author: "Joris Van Meenen"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Setup

## Load modules

```{r}
library(readxl)
library(ggplot2)
library(dplyr)
library(ggprism)
library(ggforce)
library(stringr)
library(ggpubr)
library(rstatix)
library(emmeans)
library(tidyr)
library(scales)
library(ggstatsplot)
library(sandwich)
```

## Load data

```{r}
long <- data.frame()

dir <- "D://Documents//Work//Data//Cornea-on-chip//Epithelial barrier//08_Supplements//Tecan//FITC-Dextran"

blankList <- c("JVM_FITC-Dextran (Modified)_20251119_123809.xlsx", "JVM_FITC-Dextran (Modified)_20251119_152507.xlsx")
wtfList <- c("JVM_FITC-Dextran (Modified)_20251119_155957.xlsx")

xlsxList <- list.files(path = dir, pattern = "*.xlsx", full.names = TRUE, ignore.case = TRUE)

for (xlsx in xlsxList) {
  raw <- read_xlsx(xlsx, col_names = FALSE)
  skip <- which(raw[[1]] == "<>")[1] - 1
  df <- read_xlsx(
    file.path(xlsx),
    skip = skip
  )
  df <- df[1:8,2:13]
  fluorescence <- as.vector(t(df))
  fluorescence <- fluorescence[!is.na(fluorescence) > 0]
  fluorescence<- as.numeric(fluorescence)
  
  gain <- read_xlsx(
    file.path(xlsx),
    range = "E31",
    col_names = FALSE
  )[[1]]
  gain <- rep(gain, length(fluorescence))
  
  plate <- basename(xlsx)
  plate <- rep(plate, length(fluorescence))
  
  if (basename(xlsx) %in% blankList) {
    condition <- c(
      rep(c("Control"), 9),
      rep(c("HCE-T", "Calcium"), times = 4),
      rep(c("Blank"), 4),
      rep(c("GSK", "SP"), times = 4),
      rep(c("Blank"), 4),
      rep(c("SP+IGF1", "IGF1"), times = 4),
      rep(c("HCE-T", "Calcium"), times = 4),
      rep(c("GSK", "SP"), times = 4),
      rep(c("SP+IGF1", "IGF1"), times = 4),
      rep(c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1"), each = 2)
    )
    
    replicate <- c(
      1,5,2,6,3,7,4,8,9,
      rep(1:4, each = 2),
      1:4,
      rep(1:4, each = 2),
      5:8,
      rep(1:4, each = 2),
      rep(5:8, each = 2, times = 3),
      rep(9:10, times = 6)
    )
  } else if (basename(xlsx) %in% wtfList) {
    condition <- c(
      rep(c("HCE-T", "Calcium"), times = 4),
      rep(c("Blank"), 4),
      rep(c("GSK", "SP"), times = 4),
      rep(c("Blank"), 4),
      rep(c("SP+IGF1", "IGF1"), times = 4),
      "Control",
      rep(c("HCE-T", "Calcium"), times = 4),
      rep(c("GSK", "SP"), times = 4),
      "SP+IGF1",
      "IGF1",
      rep("Control", 2),
      rep(c("HCE-T", "Calcium"), times = 2),
      rep("Control", 4),
      rep(c("GSK", "SP"), times = 2),
      rep("Control", 2),
      "SP+IGF1",
      "IGF1",
      rep(c("SP+IGF1", "IGF1"), times = 4)
    )
    
    replicate <- c(
      rep(1:4, each = 2),
      1:4,
      rep(1:4, each = 2),
      5:8,
      rep(1:4, each = 2),
      5,
      rep(5:8, each = 2, times = 2),
      rep(9, 2),
      1:2,
      rep(9:10, each = 2),
      6:7,
      3:4,
      rep(9:10, each = 2),
      8:9,
      rep(10, 2),
      rep(5:8, each = 2)
    )
  } else {
    condition <- c(
      rep(c("HCE-T", "Calcium"), times = 4),
      rep(c("Blank"), 4),
      rep(c("GSK", "SP"), times = 4),
      rep(c("Blank"), 4),
      rep(c("SP+IGF1", "IGF1"), times = 4),
      rep(c("HCE-T", "Calcium"), times = 4),
      rep(c("GSK", "SP"), times = 4),
      rep(c("SP+IGF1", "IGF1"), times = 4),
      rep(c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1"), each = 2),
      rep(c("Control"), 9)
    )
    
    replicate <- c(
      rep(1:4, each = 2),
      1:4,
      rep(1:4, each = 2),
      5:8,
      rep(1:4, each = 2),
      rep(5:8, each = 2, times = 3),
      rep(9:10, times = 6),
      1,5,2,6,3,7,4,8,9
    )
  }
  
  df <- data.frame(
    "Plate" = plate,
    "Condition" = condition,
    "Replicate" = replicate,
    "Fluorescence (RFU)" = fluorescence, 
    "Gain" = gain,
    check.names = FALSE
  )

  long <- dplyr::bind_rows(long, df)
}

timepoint <- c(rep(c(seq(0, 40, by = 5), 0, 5, 40), each = length(fluorescence)))
  
PBS <- c(rep("Before PBS", 9*length(fluorescence)), rep("After PBS", 3*length(fluorescence)))


long["PBS"] <- PBS
long["Time (min)"] <- timepoint

## Set to factor to enable statistics bracket placement
long$Condition <- factor(long$Condition, levels = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1", "Control", "Blank"))

long
```

# Raw data

## Visualisation

The optimal gain was automatically determined for each timepoint, leading to a seemingly decrease of Blank values after PBS was added.

```{r}
dat <- long

ggplot(data = dat, aes(x = `Time (min)`, y = `Fluorescence (RFU)`, color = Condition, group = interaction(Replicate, Condition))) +
  scale_y_continuous(trans = "log2") +
  geom_line(aes(linewidth = (Condition == "Blank" | Condition == "Control"))) +
  scale_linewidth_manual(
    values = c("TRUE" = 1.5, "FALSE" = 0.5),
    guide = "none"
  ) +
  facet_wrap(~ reorder(PBS, desc(PBS)))
```

# Normalised data

## Normalisation

Normalise to blanks to be able to compare different plates with different gains

```{r}

## Normalise by blank samples
long <- long %>%
  group_by(PBS, `Time (min)`) %>%
  mutate(
    Blank = mean(`Fluorescence (RFU)`[Condition == "Blank"], na.rm = TRUE),
    `Blank Normalised Fluorescence (AU)` = `Fluorescence (RFU)` / Blank
  ) %>%
  ungroup()

## Normalise by timepoint = 0
long <- long %>%
  group_by(PBS, Condition, Replicate) %>%
  mutate(
    Time0 = `Blank Normalised Fluorescence (AU)`[[1]],
    `Normalised Fluorescence (AU)` = `Blank Normalised Fluorescence (AU)` / Time0
  ) %>%
  ungroup()

  
```

## Visualise Normalised data

-   [ ] Adjust line thickness in legend

```{r, fig.height=4, fig.width=8}
dat <- long

ggplot(data = dat, aes(x = `Time (min)`, y = `Blank Normalised Fluorescence (AU)`, color = Condition, group = interaction(Replicate, Condition))) +
  scale_y_continuous(trans = "log2") +
  geom_line(aes(linewidth = (Condition == "Blank" | Condition == "Control"))) +
  scale_linewidth_manual(
    values = c("TRUE" = 1.5, "FALSE" = 0.5),
    guide = "none"
  ) +
  facet_wrap(~ reorder(PBS, desc(PBS))) +
  theme_prism() +
  theme(aspect.ratio = 0.713)

dat <- long

ggplot(data = dat, aes(x = `Time (min)`, y = `Normalised Fluorescence (AU)`, color = Condition, group = interaction(Replicate, Condition))) +
  scale_y_continuous(trans = "log2") +
  geom_line(aes(linewidth = (Condition == "Blank" | Condition == "Control"))) +
  scale_linewidth_manual(
    values = c("TRUE" = 1.5, "FALSE" = 0.5),
    guide = "none"
  ) +
  facet_wrap(~ reorder(PBS, desc(PBS))) +
  theme_prism() +
  theme(aspect.ratio = 0.713)
```

# Calculate metrics

```{r}

metrics <- long[long$`Time (min)` >= 5 & long$Condition != "Blank",] %>%
  group_by(Condition, Replicate) %>%
  summarise(
    `Slope (AU/min)` = coefficients(lm(`Blank Normalised Fluorescence (AU)` ~ `Time (min)`))[2]
  ) %>%
  ungroup()

normalisedMetrics <- metrics %>%
  mutate(
    `Normalised slope (AU)` = `Slope (AU/min)` / mean(`Slope (AU/min)`[Condition == "Control"])
  )
```

## Statistics

```{r}
dat <- normalisedMetrics[normalisedMetrics$Condition != "Control",]
renamed_dat <- dat %>%
  rename(Slope = `Normalised slope (AU)`)

model <- lm(`Normalised slope (AU)` ~ Condition, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`Normalised slope (AU)`",
         facet.by = "Condition",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Condition) %>%
  shapiro_test(Slope)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`Normalised slope (AU)` ~ Condition)
dat_summary <- dat %>%
  group_by(Condition) %>%
  get_summary_stats(`Normalised slope (AU)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_normalised <- emmeans(model, ~ Condition, vcov. = vcovHC3)
pairs(emm_normalised, adjust = "bonferroni")
stat_normalised <- summary(pairs(emm_normalised, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_normalised_pos <- stat_normalised %>%
  add_xy_position(
    x = "Condition",
    data = dat,
    formula = `Normalised slope (AU)` ~ Condition,
  ) %>%
  mutate(y.position = 0.15 + (row_number() * 0.05)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Condition))),
    xmax = match(group2, levels(droplevels(dat$Condition))),
  )
```

## Visualisation

```{r}
dat <- normalisedMetrics[normalisedMetrics$Condition != "Control",]
x <- dat$Condition
y <- dat$`Normalised slope (AU)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 4, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  geom_hline(yintercept = 1, linetype="dashed") +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_normalised_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("HCE-T", "Calcium", "GSK", "SP", "SP+IGF1", "IGF1", "Control", "Calibration resistor", "Measurement medium"),
    values = c("HCE-T" = "#F8766D", "Calcium" = "#DB8E00", "GSK" = "#AEA200", "SP" = "#64B200", "SP+IGF1" = "#00BD5C", "IGF1" = "#00C1A7", "Control" = "#00BADE", "Blank" = "#00A6FF")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())
```
