---
title: "09_ALI-TEER"
author: "Joris Van Meenen"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Setup

## Load modules

```{r}
library(dplyr)
library(ggplot2)
library(ggprism)
library(ggforce)
library(tidyr)
library(scales)
library(rstatix)
library(ggpubr)
library(emmeans)
library(sandwich)
library(zoo)
library(stringr)

set.seed(42)
```

## Platemap

```{r}



plate <- c(rep(1:2, each = 24), rep(3, 12), rep(4, 20))
row <- c(rep(1:4, each = 6, times = 2), rep(2:3, each = 6), rep(1:4, each = 5))
column <- c(rep(1:6, times = 10), rep(1:5, times = 4))
condition <- c(rep(c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry"), times = 10), rep("Control", 5), rep("Shear stress", 10), rep("Control", 5))

df <- data.frame(Plate = plate, Row = row, Column = column, Condition = condition)


dat <- df
dat$Plate <- paste0("Plate ", as.character(dat$Plate))
x <- dat$Column
y <- dat$Row

ggplot(data = dat, aes(x = factor(Column), y = reorder(Row, desc(Row)), color = factor(Condition, levels = c("HCE-T", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Hydrogel control")))) + 
  geom_point(shape = 16, size = 28) +
  #scale_fill_continuous(limits = c(min(dat$`Resistance (Ω)`[dat$`Resistance (Ω)` > 300]), max(z$`Resistance (Ω)`))) +
  xlab(names(which(sapply(dat, identical, y = x)))) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_color_manual(
    breaks = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Calibration resistor", "Measurement medium", "Artificial tears"),
    values = c("HCE-T" = "#F8766D", "Hydrogel control" = "#DB8E00", "Hydrogel HCE-T" = "#AEA200", "Tears" = "#64B200", "ALI hydrated" = "#00BD5C", "ALI dry" = "#00C1A7", "Shear stress" = "#00BADE", "Control" = "#00A6FF", "Calibration resistor" = "#B385FF", "Measurement medium" = "#EF67EB", "Artificial tears" = "#FF63B6")) +
  facet_wrap(~ Plate) +
  theme_prism(base_size = 28) +
  theme(
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    legend.key.spacing.y = unit(-1, "lines")
  )
```

## Data to long

```{r}
## Initialise variables
long <- data.frame()
startDate <- as.Date("20260204", format="%Y%m%d")
dir = "D://Documents//Work//Data//Cornea-on-chip//Epithelial barrier//09_ALI//EVOM3//"

## Load and concatenate csv files
csvList = list.files(path = dir, pattern = "*.CSV", full.names = TRUE)

for (csv in csvList) {
  ## Extract resistance values
  df <- read.csv(
    file.path(csv),
    skip = 7,
    header = TRUE,
    stringsAsFactors = FALSE,
    check.names = FALSE
  )
  df <- df[1:8,2:13]
  resistance <- as.vector(t(df))
  resistance <- resistance[resistance > 0]
  df <- data.frame("Resistance (Ω)" = resistance, check.names = FALSE)
  ## Filter out calibration measurements
  df <- df %>% 
    mutate(
      Condition = case_when(
        (row_number() == 1 & `Resistance (Ω)` >= 995 & `Resistance (Ω)` <= 1005) ~ "Calibration resistor",
        (`Resistance (Ω)` >= 30 & `Resistance (Ω)` <= 50) ~ "Measurement medium",
        (row_number() == length(resistance) & `Resistance (Ω)` >= 90 & `Resistance (Ω)` <= 110) ~ "Artificial tears",
        TRUE ~ "TBD"
      ),
      ## Each medium measurement designates a separate set of measurements
      Measurement = cumsum(Condition == "Measurement medium")
    )
  
  ## Add date and day variables
  name <- basename(csv)
  date <- as.Date(strsplit(name, "_")[[1]][2], format="%Y%m%d")
  dateDiff <- as.double(date - startDate)
  df["Date"] <- rep(date, nrow(df))
  df["Days after seeding"] <- rep(dateDiff, nrow(df))
  index <- as.integer(substr(csv, nchar(csv) - 4, nchar(csv)-4))
  
  ## Plate layouts
  plate <- c(rep(c(1, 2), each = 4), rep(3, 2), rep(c(rep(1, 5), 4), times = 4), rep(c(rep(2, 5), 4), times = 4), rep(c(rep(3, 5), 4), times = 2))
  row <- c(1:4, 1:4, 2:3, c(rep(1, 5), 2, rep(2, 6), rep(3, 5), 2, rep(4, 5), 2, rep(1, 5), 2, rep(2, 5), 3, rep(3, 6), rep(4, 5), 3, rep(2, 5), 3, rep(3, 6)))
  column <- c(rep(2, 10),  rep(c(1, 3:6, 1, 1, 3:6, 2, 1, 3:6, 3, 1, 3:6, 4, 1, 3:6, 5), times = 2))
  replicate <- c(1:10, rep(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), each = 6))
  condition <- c(rep("Hydrogel control", 10), rep(c("HCE-T", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress"), times = 10))

  ## Endpoint (20/02/2026 - 23/02/2026)
  if (df[1, "Date"] >= as.Date("2026-02-20")) {
    
    df[df$Condition == "TBD", "Plate"] <- c(rep(4, 10), plate)
    df[df$Condition == "TBD", "Row"] <- c(rep(1, 5), rep(4, 5), row)
    df[df$Condition == "TBD", "Column"] <- c(rep(1:5, times = 2), column)
    df[df$Condition == "TBD", "Replicate"] <- c(1:10, replicate)
    df["Time (min)"] <- rep(c(20, 145, 40)[index], length(resistance))
    df[df$Condition == "TBD", "Condition"] <- c(rep("Control", 10), condition)
    
  } else {
    
    ### During conditions (16/02/2026 - 18/02/2026) --FIRST-- Before vs after medium change
    if ((df[1, "Date"] >= as.Date("2026-02-16")) & (index == 1) & (df[1, "Date"] < as.Date("2026-02-20"))) {
      
      df[df$Condition == "TBD", "Plate"] <- c(rep(1, 4), rep(c(rep(1, 3), 4), times = 4), plate)
      df[df$Condition == "TBD", "Row"] <- c(1:4, rep(1, 3), 1, rep(2, 3), 1, rep(3, 3), 1, rep(4, 3), 1, row)
      df[df$Condition == "TBD", "Column"] <- c(rep(2, 4), 1, 3, 4, 1, 1, 3, 4, 2, 1, 3, 4, 3, 1, 3, 4, 4, column)
      df[df$Condition == "TBD", "Replicate"] <- c(1:4, rep(1:4, each = 4), replicate)
      df["Time (min)"] <- c(20, rep(0, 21), rep(20, 71))
      df[df$Condition == "TBD", "Condition"] <- c(rep("Hydrogel control", 4), rep(c("HCE-T", "Hydrogel HCE-T", "Tears", "Shear stress"), times = 4), condition)
      
    } else {
      
        df[df$Condition == "TBD", "Plate"] <- plate
        df[df$Condition == "TBD", "Row"] <- row
        df[df$Condition == "TBD", "Column"] <- column
        df[df$Condition == "TBD", "Replicate"] <- replicate
        df["Time (min)"] <- rep(c(20, 40, 60, 80)[index], length(resistance))
        df[df$Condition == "TBD", "Condition"] <- condition
      
    }
    
  }
  
  df[is.na(df$Replicate), "Replicate"] <- 1
  

  ## Merge all csv files
  long <- dplyr::bind_rows(long, df)
}

## Set time of Artificial tears measurement to 20, for easier downstream processing (the same is done for the Calibration resistor for the same reason, which was actually measured at time 0)
long[long$Condition == "Artificial tears", "Time (min)"] <- rep(20, length(long[long$Condition == "Artificial tears", "Time (min)"]))

## Set to factor to enable statistics bracket placement
long$Condition <- factor(long$Condition, levels = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Calibration resistor", "Measurement medium", "Artificial tears"))

long <- long %>%
  mutate(Group = case_when(
    Condition %in% c("Hydrogel control", "Control", "Calibration resistor", "Measurement medium", "Artificial tears") ~ "No cells",
    TRUE ~ "Cells"
  ))


long
```

## Filter outliers

Filtered based on visual inspection of brightfield images –\> dislodged hydrogels

```{r}

long <- long %>%
  filter(!(Condition == "Hydrogel HCE-T" & (Replicate == 6 | Replicate == 9)))
```

# Resistance

## Visualise data across days

```{r}
dat <- long[long$`Time (min)` == 20,]

control_conditions <- c("Calibration resistor", "Measurement medium", "Artificial tears", "Control")
interesting_conditions <- setdiff(unique(dat$Condition), control_conditions)
dat_background <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_facet = Condition) %>%
  crossing(Condition_display = interesting_conditions) %>%
  filter(Condition_facet != Condition_display)
dat_interesting <- dat %>%
  filter(Condition %in% interesting_conditions) %>%
  mutate(Condition_display = Condition)
dat_control <- dat %>%
  filter(Condition %in% control_conditions) %>%
  crossing(Condition_display = interesting_conditions)
dat_interesting <- rbind(dat_interesting, dat_control)

ggplot(data = dat, aes(x = `Days after seeding`, y = `Resistance (Ω)`, color = Condition)) + 
  geom_line(data = dat_background, aes(group = interaction(Condition_facet, Replicate)), color = "grey") +
  geom_point(data = dat_background, aes(group = interaction(Condition_facet, Replicate)), color = "grey", size = 2) +
  geom_line(data = dat_interesting, aes(group = interaction(Condition, Replicate))) +
  geom_point(data = dat_interesting, aes(group = interaction(Condition, Replicate)), size = 2) +
  geom_hline(yintercept = 0, linetype="dashed") +
  #geom_vline(xintercept = 9, linetype="dashed") +
  #annotate("text", x=9, y=3250, label="Start", vjust = -0.5, angle = 90) +
  geom_vline(xintercept = 16, linetype="dashed") +
  annotate("text", x = 16, y = 3250, label = "Diffusion", vjust = -0.5, angle = 90) +
  geom_vline(xintercept = 19, linetype="dashed") +
  annotate("text", x = 19, y = 3250, label = "Viability", vjust = -0.5, angle = 90) +
  scale_y_continuous(limits = c(-500, 4000), expand = c(0, 0), oob = scales::oob_keep, guide = guide_prism_minor()) +
  scale_x_continuous(limits = c(0, 20), expand = c(0, 0), guide = guide_prism_minor(), minor_breaks = seq(0, 20, 1)) +
  scale_color_manual(
    breaks = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Calibration resistor", "Measurement medium", "Artificial tears"),
    values = c("HCE-T" = "#F8766D", "Hydrogel control" = "#DB8E00", "Hydrogel HCE-T" = "#AEA200", "Tears" = "#64B200", "ALI hydrated" = "#00BD5C", "ALI dry" = "#00C1A7", "Shear stress" = "#00BADE", "Control" = "#00A6FF", "Calibration resistor" = "#B385FF", "Measurement medium" = "#EF67EB", "Artificial tears" = "#FF63B6")) +
  facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress")), scales = "free") +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(panel.spacing.x = unit(1.5, "lines"), legend.key.spacing.y = unit(0.5, "lines"))

 

```

## Metrics: CV

Plateau period is from Day 9 to day 14 with a new plateau period starting at day 21.

```{r}
dat <- long[!is.na(long$Plate) & long$`Time (min)` == 20,]
cv <- dat %>%
  filter(!is.na(Plate)) %>%
  group_by(Condition, Replicate) %>%
  arrange(`Days after seeding`) %>%
  mutate(CV = rollapply(
    data = `Resistance (Ω)`,
    width = 3,
    FUN = function(x) {
      sd(x)/mean(x) * 100
    },
    align = "right",
    fill = NA
  )) %>%
  ungroup() %>% 
  mutate(`CV <= 15%` = case_when(
    CV <= 15 ~ TRUE,
    CV > 15 ~ FALSE,
    TRUE ~ NA
  ))
```

## Visualisation: CV

```{r}
dat <- cv[cv$Condition != "Control",]
x <- factor(dat$Replicate)
y <- reorder(dat$`Days after seeding`, desc(dat$`Days after seeding`))

ggplot(data = dat, aes(x = x, y = y, color = `CV <= 15%`)) + 
  geom_point(shape = 16, size = 8) +
  xlab("Replicate") +
  ylab("Days after seeding") +
  facet_wrap(~ Condition) +
  theme_prism(base_size = 22, base_line_size = 1.2) +
  theme(axis.line = element_blank(), axis.ticks = element_blank(), panel.spacing.x = unit(1.5, "lines"), legend.title = element_text(), legend.title.position = "top")
```

### Check effect medium change

```{r, fig.height=8, fig.width=12}

dat <- long[long$`Time (min)` <= 20 & long$Date >= as.Date("2026-02-16") & long$Date < as.Date("2026-02-20") & long$Replicate <= 4 & long$Condition != "Calibration resistor" & long$Condition != "ALI hydrated" & long$Condition != "ALI dry" & long$Condition != "Artificial tears" & long$Condition != "Measurement medium",]

dat$`Days after seeding` <- factor(dat$`Days after seeding`, levels = c(12, 14))
dat$`Days after seeding` <- factor(paste0("Day ", as.character(dat$`Days after seeding`)), levels = c("Day 12","Day 14"))

ggplot(data = dat, aes(x = factor(`Time (min)`), y = `Resistance (Ω)`, color = Condition, group = interaction(Condition, Measurement))) + 
    xlab("Measurement") +
    scale_x_discrete(label = c("Before", "After")) +
    geom_violin(width = 0.5, scale = "width", position = position_dodge(width = 0.8), alpha = 0.2, colour = "black", linewidth = 1) +
    geom_sina(size = 4, maxwidth = 0.5, position = position_dodge(width = 0.8), scale = FALSE, alpha = 0.4, stroke = 0) +
    facet_wrap(~ `Days after seeding`) +
    theme_prism(base_size = 28) +
    theme(axis.title.x = element_blank())

```

### Check stability across minutes

```{r, fig.height=12, fig.width=12}
#dat <- long[long$`Time (min)` <= 80 & long$PBS == "Before PBS",]
dat <- long[long$`Time (min)` >= 20 & long$`Time (min)` <= 80 & long$Date >= as.Date("2026-02-16") & long$Date < as.Date("2026-02-20") & long$Condition != "Calibration resistor" & long$Condition != "Artificial tears",]

dat$`Days after seeding` <- factor(dat$`Days after seeding`, levels = c(12, 14))
dat$`Days after seeding` <- factor(paste0("Day ", as.character(dat$`Days after seeding`)), levels = c("Day 12","Day 14"))

lapply(split(dat, dat$`Days after seeding`), function(z) {
  control_conditions <- c("Calibration resistor", "Measurement medium", "Artificial tears")
  interesting_conditions <- setdiff(unique(z$Condition), control_conditions)
  dat_background <- z %>%
    filter(Condition %in% interesting_conditions) %>%
    mutate(Condition_facet = Condition) %>%
    crossing(Condition_display = interesting_conditions) %>%
    filter(Condition_facet != Condition_display)
  dat_interesting <- z %>%
    filter(Condition %in% interesting_conditions) %>%
    mutate(Condition_display = Condition)
  dat_control <- z %>%
    filter(Condition %in% control_conditions) %>%
    crossing(Condition_display = interesting_conditions)

  ggplot(data = z, aes(x = `Time (min)`, y = `Resistance (Ω)`)) + 
    geom_line(data = dat_background,
              aes(group = interaction(Condition_facet, Replicate)),
              color = "grey") +
    geom_point(data = dat_background,
              aes(group = interaction(Condition_facet, Replicate)),
              color = "grey") +
    geom_line(data = dat_interesting,
              aes(color = Condition, 
                  group = interaction(Condition, Replicate))
              ) +
    geom_point(data = dat_interesting,
              aes(color = Condition, 
                  group = interaction(Condition, Replicate))
              ) +
    geom_line(data = dat_control,
              aes(color = Condition, 
                  group = interaction(Condition, Replicate))
              ) +
    geom_point(data = dat_control,
              aes(color = Condition, 
                  group = interaction(Condition, Replicate))
              ) +
    geom_hline(yintercept = 1000, linetype="dashed") +
    facet_wrap(~ factor(Condition_display, levels = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress"))) +
    theme_prism() +
    theme(aspect.ratio = 0.713) +
    labs(title = z$`Days after seeding`)
})

# Can do linear fit and show this in color while only showing the condition-specific points

```

### Visualise controls

```{r}

#dat <- long[long$`Time (min)` == 20 & long$PBS == "Before PBS" & long$Condition == "Control" & long$Replicate != 2,]
dat <- long[long$`Time (min)` == 20 & long$Condition == "Control",]
x <- rep("Experiment 2", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(200, 400), expand = c(0, 0)) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())
```

## Metrics: nTEER

Control and incubation in PBS only at day 16 after cell seeding

```{r}

control <- mean(long[long$Date == as.Date("2026-02-20"),]$`Resistance (Ω)`[long[long$Date == as.Date("2026-02-20"),]$Condition == "Control"])
hydrogelcontrol <- mean(long[long$Date == as.Date("2026-02-20"),]$`Resistance (Ω)`[long[long$Date == as.Date("2026-02-20"),]$Condition == "Hydrogel control"])

nTEER <- long[long$Date == as.Date("2026-02-20"),] %>%
  filter(!is.na(Plate)) %>%
  group_by(Date, `Days after seeding`, Condition, Replicate) %>%
  reframe(
    `TEER (Ω*cm²)` = case_when(
      str_detect(first(Condition), "Hydrogel HCE-T") ~ (`Resistance (Ω)`[`Time (min)` == 20] - hydrogelcontrol) * 0.3359273609,
      TRUE ~ (`Resistance (Ω)`[`Time (min)` == 20] - control) * 0.3359273609
    ),
    `nTEER (Ω*cm²)` = (`Resistance (Ω)`[`Time (min)` == 20] - `Resistance (Ω)`[`Time (min)` == 40]) * 0.3359273609
  )
```

## Statistics TEER

```{r}

dat <- nTEER[nTEER$Condition != "Control" & nTEER$Condition != "Hydrogel control",]
renamed_dat <- dat %>%
  rename(TEER = `TEER (Ω*cm²)`)

model <- lm(`TEER (Ω*cm²)` ~ Condition, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`TEER (Ω*cm²)`",
         facet.by = "Condition",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Condition) %>%
  shapiro_test(TEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`TEER (Ω*cm²)` ~ Condition)
dat_summary <- dat %>%
  group_by(Condition) %>%
  get_summary_stats(`TEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_TEER <- emmeans(model, ~ Condition, vcov. = vcovHC3)
pairs(emm_TEER, adjust = "bonferroni")
stat_TEER <- summary(pairs(emm_TEER, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_TEER_pos <- stat_TEER %>%
  add_xy_position(
    x = "Condition",
    data = dat,
    formula = `TEER (Ω*cm²)` ~ Condition,
  ) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Condition))),
    xmax = match(group2, levels(droplevels(dat$Condition))),
  )

```

## Statistics nTEER

HCE-T as an outlier that needs taken care of

```{r}

dat <- nTEER[nTEER$Condition != "Control" & nTEER$Condition != "Hydrogel control" & !(nTEER$Condition == "HCE-T" & nTEER$Replicate == 8 ),]
renamed_dat <- dat %>%
  rename(nTEER = `nTEER (Ω*cm²)`)

model <- lm(`nTEER (Ω*cm²)` ~ Condition, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`nTEER (Ω*cm²)`",
         facet.by = "Condition",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Condition) %>%
  shapiro_test(nTEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`nTEER (Ω*cm²)` ~ Condition)
dat_summary <- dat %>%
  group_by(Condition) %>%
  get_summary_stats(`nTEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_nTEER <- emmeans(model, ~ Condition, vcov. = vcovHC3)
pairs(emm_nTEER, adjust = "bonferroni")
stat_nTEER <- summary(pairs(emm_nTEER, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_nTEER_pos <- stat_nTEER %>%
  add_xy_position(
    x = "Condition",
    data = dat,
    formula = `nTEER (Ω*cm²)` ~ Condition,
  ) %>%
  mutate(y.position = 375 + (row_number() * 25)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Condition))),
    xmax = match(group2, levels(droplevels(dat$Condition))),
  )

```

## Visualise (n)TEER

```{r, fig.width=12, fig.height=12}

dat <- long[long$`Time (min)` == 20 & long$Date == as.Date("2026-02-20") & long$Condition != "Calibration resistor" & long$Condition != "Measurement medium" & long$Condition != "Artificial tears",]
#dat <- long[long$`Time (min)` == 20 & long$Date == as.Date("2026-02-20") & str_detect(long$Condition, regex("Control|Hydrogel|HCE-T", ignore_case = TRUE)),]
x <- dat$Condition
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 1) +
  geom_sina(size = 2, maxwidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(0, 2000), expand = c(0, 0)) +
  theme_prism() +
  theme(aspect.ratio = 0.713, axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

dat <- nTEER[nTEER$Condition != "Control" & nTEER$Condition != "Hydrogel control",]
x <- dat$Condition
y <- dat$`TEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 2, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(0, 1000), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_TEER_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Calibration resistor", "Measurement medium", "Artificial tears"),
    values = c("HCE-T" = "#F8766D", "Hydrogel control" = "#DB8E00", "Hydrogel HCE-T" = "#AEA200", "Tears" = "#64B200", "ALI hydrated" = "#00BD5C", "ALI dry" = "#00C1A7", "Shear stress" = "#00BADE", "Control" = "#00A6FF", "Calibration resistor" = "#B385FF", "Measurement medium" = "#EF67EB", "Artificial tears" = "#FF63B6")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

dat <- nTEER[nTEER$Condition != "Control" & nTEER$Condition != "Hydrogel control" & !(nTEER$Condition == "HCE-T" & nTEER$Replicate == 8 ),]
x <- dat$Condition
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(0, 800), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_nTEER_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Calibration resistor", "Measurement medium", "Artificial tears"),
    values = c("HCE-T" = "#F8766D", "Hydrogel control" = "#DB8E00", "Hydrogel HCE-T" = "#AEA200", "Tears" = "#64B200", "ALI hydrated" = "#00BD5C", "ALI dry" = "#00C1A7", "Shear stress" = "#00BADE", "Control" = "#00A6FF", "Calibration resistor" = "#B385FF", "Measurement medium" = "#EF67EB", "Artificial tears" = "#FF63B6")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

```

# Meta

## Measurement medium

### Data

Filtering datapoints after incubation in PBS on Day 16, otherwise all timepoints are kept because non-biological samples do not change over time

```{r}

experiment4_medium <- long[!(long$`Days after seeding` == 16 & long$`Time (min)` == 40) & long$Condition == "Measurement medium",]

mean(long[long$Condition == "Artificial tears",]$`Resistance (Ω)`) - mean(experiment4_medium$`Resistance (Ω)`)

```

### Visualisation

```{r}
dat <- experiment4_medium
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())
```

### Statistics: resistance

-   Categorical variables: Experiment
-   Continuous variables: Resistance

qqplot - Experiment 2 has a worse CI

shapiro - Only Experiment 2 is considered normally distributed, but qq plots overrule this test

levene - Homogeneity of variances, the biggest difference is a factor of 2

anova: type 2, hc3 to correct for heteroscedasticity, bonferroni pairwise contrasts - No Significant effect of Experiment - All pairwise contrasts non-significant

```{r}
medium_resistance <- data.frame(
  "Experiment" = c(rep("Experiment 1", nrow(experiment1_medium)), rep("Experiment 2", nrow(experiment2_medium)), rep("Experiment 3", nrow(experiment3_medium)), rep("Experiment 4", nrow(experiment4_medium))),
  "Resistance (Ω)" = c(experiment1_medium$`Resistance (Ω)`, experiment2_medium$`Resistance (Ω)`, experiment3_medium$`Resistance (Ω)`, experiment4_medium$`Resistance (Ω)`),
  check.names = FALSE
)
dat <- medium_resistance
dat$Experiment <- as.factor(dat$Experiment)
renamed_dat <- dat %>%
  rename(Resistance = `Resistance (Ω)`)

model <- lm(`Resistance (Ω)` ~ Experiment, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`Resistance (Ω)`",
         facet.by = "Experiment",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Experiment) %>%
  shapiro_test(Resistance)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`Resistance (Ω)` ~ Experiment)
dat_summary <- dat %>%
  group_by(Experiment) %>%
  get_summary_stats(`Resistance (Ω)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_Resistance <- emmeans(model, ~ Experiment, vcov. = vcovHC3)
pairs(emm_Resistance, adjust = "bonferroni")
stat_Resistance <- summary(pairs(emm_Resistance, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_Resistance_pos <- stat_Resistance %>%
  add_xy_position(
    x = "Experiment",
    data = dat,
    formula = `Resistance (Ω)` ~ Experiment,
  ) %>%
  mutate(y.position = 50 + (row_number() * 3)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Experiment))),
    xmax = match(group2, levels(droplevels(dat$Experiment))),
  )



```

### Visualisation

```{r}
dat <- medium_resistance
x <- dat$Experiment
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Experiment)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(30, 70), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_Resistance_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("Experiment 1", "Experiment 2", "Experiment 3", "Experiment 4"),
    values = c("Experiment 1" = "#F8766D", "Experiment 2" = "#DB8E00", "Experiment 3" = "#AEA200", "Experiment 4" = "#64B200")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())
```

## Controls

### Data

Filtering datapoints after incubation in PBS on Day 16, otherwise all timepoints are kept because non-biological samples do not change over time

```{r}

experiment4_control <- long[!(long$`Days after seeding` == 16 & long$`Time (min)` == 40) & long$Condition == "Control",]

```

### Visualisation

```{r}
dat <- experiment4_control
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(200, 400), expand = c(0, 0)) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

```

### Statistics: resistance

-   Categorical variables: Experiment
-   Continuous variables: Resistance

qqplot - No comments

shapiro - Only Experiment 4 is considered normally distributed, but qq plots overrule this test

levene - Homogeneity of variances, the biggest difference is a factor of 1

anova: type 2, hc3 to correct for heteroscedasticity, bonferroni pairwise contrasts - Significant effect of Experiment - All pairwise contrasts are significant

```{r}
control_resistance <- data.frame(
  "Experiment" = c(rep("Experiment 1", nrow(experiment1_control)), rep("Experiment 3", nrow(experiment3_control)), rep("Experiment 4", nrow(experiment4_control))),
  "Resistance (Ω)" = c(experiment1_control$`Resistance (Ω)`, experiment3_control$`Resistance (Ω)`, experiment4_control$`Resistance (Ω)`),
  check.names = FALSE
)
dat <- control_resistance
dat$Experiment <- as.factor(dat$Experiment)
renamed_dat <- dat %>%
  rename(Resistance = `Resistance (Ω)`)

model <- lm(`Resistance (Ω)` ~ Experiment, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`Resistance (Ω)`",
         facet.by = "Experiment",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Experiment) %>%
  shapiro_test(Resistance)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`Resistance (Ω)` ~ Experiment)
dat_summary <- dat %>%
  group_by(Experiment) %>%
  get_summary_stats(`Resistance (Ω)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_Resistance <- emmeans(model, ~ Experiment, vcov. = vcovHC3)
pairs(emm_Resistance, adjust = "bonferroni")
stat_Resistance <- summary(pairs(emm_Resistance, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_Resistance_pos <- stat_Resistance %>%
  add_xy_position(
    x = "Experiment",
    data = dat,
    formula = `Resistance (Ω)` ~ Experiment,
  ) %>%
  mutate(y.position = 300 + (row_number() * 20)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Experiment))),
    xmax = match(group2, levels(droplevels(dat$Experiment))),
  )



```

### Visualisation

```{r}
dat <- control_resistance
x <- dat$Experiment
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Experiment)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(200, 400), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_Resistance_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("Experiment 1", "Experiment 2", "Experiment 3", "Experiment 4"),
    values = c("Experiment 1" = "#F8766D", "Experiment 2" = "#DB8E00", "Experiment 3" = "#AEA200", "Experiment 4" = "#64B200")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

```

## HCE-T

### Data

Limiting data points to the 20 minute mark for consistency Limiting non-HCE-T data points to 9 days after seeding to avoid any influence of the induced conditions Limiting data points to 16 days after seeding to avoid any influence of the diffusion assay on day 16

```{r}

experiment4_hcet_resistance <- long[long$Group == "Cells" & long$Condition != "Hydrogel HCE-T" & long$`Days after seeding` <= 9 | long$Condition == "HCE-T" & long$`Time (min)` == 20  & long$`Days after seeding` <= 16,]
experiment4_hcet_nTEER <- nTEER[nTEER$Condition == "HCE-T",]

```

### Visualisation

```{r}
dat <- experiment4_hcet_resistance
x <- rep("Experiment 1", length(dat$`Resistance (Ω)`))
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment4_hcet_nTEER
x <- rep("Experiment 1", length(dat$`TEER (Ω*cm²)`))
y <- dat$`TEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

dat <- experiment4_hcet_nTEER
x <- rep("Experiment 1", length(dat$`nTEER (Ω*cm²)`))
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5) +
  geom_sina(size = 2, maxwidth = 0.5) +
  labs(colour = "Apical volume (µL)") +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 1.4, axis.title.x = element_blank())

```

### Stat: Resistance

-   Categorical variables: Experiment
-   Continuous variables: Resistance

qqplot - Day 1 from experiment 1 causes a slight deviation from linearity - Day 2 from experiment 4 causes a slight deviation from linearity

shapiro - Only Experiment 2 is considered normally distributed, but qq plots overrule this test

levene - Heterogeneity of variances, the biggest difference is a factor of 5

anova: type 2, hc3 to correct for heteroscedasticity, bonferroni pairwise contrasts - Significant effect of Experiment - All pairwise contrasts significant except between experiment 1 and experiment 3

```{r}

## removing first timepoint makes everything significant
#experiment1_hcet_resistance <- experiment1_hcet_resistance[experiment1_hcet_resistance$`Days after seeding` >= 3,]
#experiment2_hcet_resistance <- experiment2_hcet_resistance[experiment2_hcet_resistance$`Days after seeding` >= 3,]
#experiment3_hcet_resistance <- experiment3_hcet_resistance[experiment3_hcet_resistance$`Days after seeding` >= 3,]
#experiment4_hcet_resistance <- experiment4_hcet_resistance[experiment4_hcet_resistance$`Days after seeding` >= 3,]

hcet_resistance <- data.frame(
  "Experiment" = c(rep("Experiment 1", nrow(experiment1_hcet_resistance)), rep("Experiment 2", nrow(experiment2_hcet_resistance)), rep("Experiment 3", nrow(experiment3_hcet_resistance)), rep("Experiment 4", nrow(experiment4_hcet_resistance))),
  "Resistance (Ω)" = c(experiment1_hcet_resistance$`Resistance (Ω)`, experiment2_hcet_resistance$`Resistance (Ω)`, experiment3_hcet_resistance$`Resistance (Ω)`, experiment4_hcet_resistance$`Resistance (Ω)`),
  check.names = FALSE
)
dat <- hcet_resistance
dat$Experiment <- as.factor(dat$Experiment)
renamed_dat <- dat %>%
  rename(Resistance = `Resistance (Ω)`)

model <- lm(`Resistance (Ω)` ~ Experiment, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`Resistance (Ω)`",
         facet.by = "Experiment",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Experiment) %>%
  shapiro_test(Resistance)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`Resistance (Ω)` ~ Experiment)
dat_summary <- dat %>%
  group_by(Experiment) %>%
  get_summary_stats(`Resistance (Ω)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_Resistance <- emmeans(model, ~ Experiment, vcov. = vcovHC3)
pairs(emm_Resistance, adjust = "bonferroni")
stat_Resistance <- summary(pairs(emm_Resistance, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_Resistance_pos <- stat_Resistance %>%
  add_xy_position(
    x = "Experiment",
    data = dat,
    formula = `Resistance (Ω)` ~ Experiment,
  ) %>%
  mutate(y.position = 1500 + (row_number() * 90)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Experiment))),
    xmax = match(group2, levels(droplevels(dat$Experiment))),
  )

```

### Vis: Resistance

```{r}

dat <- hcet_resistance
x <- dat$Experiment
y <- dat$`Resistance (Ω)`

ggplot(data = dat, aes(x = x, y = y, color = Experiment)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(0, 2000), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_Resistance_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("Experiment 1", "Experiment 2", "Experiment 3", "Experiment 4"),
    values = c("Experiment 1" = "#F8766D", "Experiment 2" = "#DB8E00", "Experiment 3" = "#AEA200", "Experiment 4" = "#64B200")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

```

### Stat: TEER

-   Categorical variables: Experiment
-   Continuous variables: TEER

qqplot - Day 1 from experiment 1 causes a slight deviation from linearity

shapiro - Only Experiment 1 is considered non-normally distributed, but qq plots overrule this test

levene - Heterogeneity of variances, the biggest difference is a factor of 5

anova: type 2, hc3 to correct for heteroscedasticity, bonferroni pairwise contrasts - Significant effect of Experiment - All pairwise contrasts significant except between experiment 1 and experiment 4

```{r}

hcet_TEER <- data.frame(
  "Experiment" = c(rep("Experiment 1", nrow(experiment1_hcet_TEER)), rep("Experiment 2", nrow(experiment2_hcet_nTEER)), rep("Experiment 3", nrow(experiment3_hcet_nTEER)), rep("Experiment 4", nrow(experiment4_hcet_nTEER))),
  "TEER (Ω*cm²)" = c(experiment1_hcet_TEER$`TEER (Ω*cm²)`, experiment2_hcet_nTEER$`TEER (Ω*cm²)`, experiment3_hcet_nTEER$`TEER (Ω*cm²)`, experiment4_hcet_nTEER$`TEER (Ω*cm²)`),
  check.names = FALSE
)
dat <- hcet_TEER
dat$Experiment <- as.factor(dat$Experiment)
renamed_dat <- dat %>%
  rename(TEER = `TEER (Ω*cm²)`)

model <- lm(`TEER (Ω*cm²)` ~ Experiment, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`TEER (Ω*cm²)`",
         facet.by = "Experiment",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Experiment) %>%
  shapiro_test(TEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`TEER (Ω*cm²)` ~ Experiment)
dat_summary <- dat %>%
  group_by(Experiment) %>%
  get_summary_stats(`TEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_TEER <- emmeans(model, ~ Experiment, vcov. = vcovHC3)
pairs(emm_TEER, adjust = "bonferroni")
stat_TEER <- summary(pairs(emm_TEER, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_TEER_pos <- stat_TEER %>%
  add_xy_position(
    x = "Experiment",
    data = dat,
    formula = `TEER (Ω*cm²)` ~ Experiment,
  ) %>%
  mutate(y.position = 220 + (row_number() * 20)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Experiment))),
    xmax = match(group2, levels(droplevels(dat$Experiment))),
  )

```

### Vis: TEER

TEER of Experiment 2 is estimated using the mean control across all experiments

```{r}

dat <- hcet_TEER
x <- dat$Experiment
y <- dat$`TEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Experiment)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(-50, 400), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  geom_hline(yintercept = 0, linetype="dashed") +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_TEER_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("Experiment 1", "Experiment 2", "Experiment 3", "Experiment 4"),
    values = c("Experiment 1" = "#F8766D", "Experiment 2" = "#DB8E00", "Experiment 3" = "#AEA200", "Experiment 4" = "#64B200")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

```

### Stat: nTEER

-   Categorical variables: Experiment
-   Continuous variables: nTEER

qqplot - No comments

shapiro - Only Experiment 3 is considered normally distributed, but qq plots overrule this test

levene - Heterogeneity of variances, the biggest difference is a factor of 2

anova: type 2, hc3 to correct for heteroscedasticity, bonferroni pairwise contrasts - Significant effect of Experiment - All pairwise contrasts significant except between experiment 2 and experiment 4

```{r}
hcet_nTEER <- data.frame(
  "Experiment" = c(rep("Experiment 1", nrow(experiment1_hcet_nTEER)), rep("Experiment 2", nrow(experiment2_hcet_nTEER)), rep("Experiment 3", nrow(experiment3_hcet_nTEER)), rep("Experiment 4", nrow(experiment4_hcet_nTEER))),
  "nTEER (Ω*cm²)" = c(experiment1_hcet_nTEER$`nTEER (Ω*cm²)`, experiment2_hcet_nTEER$`nTEER (Ω*cm²)`, experiment3_hcet_nTEER$`nTEER (Ω*cm²)`, experiment4_hcet_nTEER$`nTEER (Ω*cm²)`),
  check.names = FALSE
)
dat <- hcet_nTEER
dat$Experiment <- as.factor(dat$Experiment)
renamed_dat <- dat %>%
  rename(nTEER = `nTEER (Ω*cm²)`)

model <- lm(`nTEER (Ω*cm²)` ~ Experiment, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`nTEER (Ω*cm²)`",
         facet.by = "Experiment",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Experiment) %>%
  shapiro_test(nTEER)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`nTEER (Ω*cm²)` ~ Experiment)
dat_summary <- dat %>%
  group_by(Experiment) %>%
  get_summary_stats(`nTEER (Ω*cm²)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_nTEER <- emmeans(model, ~ Experiment, vcov. = vcovHC3)
pairs(emm_nTEER, adjust = "bonferroni")
stat_nTEER <- summary(pairs(emm_nTEER, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_nTEER_pos <- stat_nTEER %>%
  add_xy_position(
    x = "Experiment",
    data = dat,
    formula = `nTEER (Ω*cm²)` ~ Experiment,
  ) %>%
  mutate(y.position = 220 + (row_number() * 20)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Experiment))),
    xmax = match(group2, levels(droplevels(dat$Experiment))),
  )

```

### Vis: nTEER

```{r}

dat <- hcet_nTEER
x <- dat$Experiment
y <- dat$`nTEER (Ω*cm²)`

ggplot(data = dat, aes(x = x, y = y, color = Experiment)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(-50, 400), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  geom_hline(yintercept = 0, linetype="dashed") +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_nTEER_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  scale_color_manual(
    breaks = c("Experiment 1", "Experiment 2", "Experiment 3", "Experiment 4"),
    values = c("Experiment 1" = "#F8766D", "Experiment 2" = "#DB8E00", "Experiment 3" = "#AEA200", "Experiment 4" = "#64B200")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())

```
