---
title: "09_ALI-PrestoBlue"
author: "Joris Van Meenen"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

## Load modules

```{r}
library(readxl)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(ggprism)
library(ggforce)
library(rstatix)
library(emmeans)
library(tidyr)
library(scales)
library(ggstatsplot)
library(sandwich)
#library(nlme)

set.seed(42)
```

## Load data

```{r}
long <- data.frame()

dir <- "D://Documents//Work//Data//Cornea-on-chip//Epithelial barrier//09_ALI//PrestoBlue"

xlsxList <- list.files(path = dir, pattern = "*.xlsx", full.names = TRUE, ignore.case = TRUE)

for (xlsx in xlsxList) {
  df <- read_xlsx(
    file.path(xlsx),
    skip = 44
  )
  df <- df[1:8,2:13]
  fluorescence <- as.vector(t(df))
  fluorescence <- fluorescence[!is.na(fluorescence) > 0]
  fluorescence<- as.numeric(fluorescence)
  
  plate <- c(
    c(rep(1, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(1, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(1, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(1, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(2, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(2, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(2, 6), rep(4, 2), rep(3, 2), NA),
    c(rep(2, 6), rep(4, 2), rep(3, 2), NA)
  )
  
  condition <- c(
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Control", "Shear stress", "Control", "Control", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Shear stress", "Shear stress", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Control", "Shear stress", "ALI dry", "ALI dry", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Control", "Shear stress", "ALI hydrated", "ALI hydrated", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Control", "Shear stress", "Tears", "Tears", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Hydrogel HCE-T", "Hydrogel HCE-T", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Hydrogel control", "Hydrogel control", "Reservoir"),
    c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "HCE-T", "HCE-T", "Reservoir")
  )
  
  replicate <- c(
    c(rep(1, 8), 9, 10, 1),
    c(rep(2, 8), 9, 10, 2),
    c(rep(3, 8), 9, 10, 3),
    c(rep(4, 8), 9, 10, 4),
    c(rep(5, 8), 9, 10, 5),
    c(rep(6, 8), 9, 10, 6),
    c(rep(7, 8), 9, 10, 7),
    c(rep(8, 8), 9, 10, 8)
  )
  
  df <- data.frame(
    "Plate" = plate,
    "Condition" = condition,
    "Replicate" = replicate,
    "Fluorescence (RFU)" = fluorescence, 
    check.names = FALSE
  )

  long <- dplyr::bind_rows(long, df)
}

long$Condition <- factor(long$Condition, levels = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Reservoir"))

long <- long %>%
  mutate(Group = case_when(
    Condition %in% c("Hydrogel control", "Control", "Reservoir") ~ "No cells",
    TRUE ~ "Cells"
  ))
```

## Visualisation: Data

```{r, fig.width=12, fig.width=12}
dat <- long
x <- dat$Condition
y <- dat$`Fluorescence (RFU)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 1) +
  geom_sina(size = 2, maxwidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  theme_prism() +
  theme(aspect.ratio = 0.713, axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())


ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(2000, 55000), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  scale_color_manual(
    breaks = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Reservoir", "Measurement medium", "Artificial tears"),
    values = c("HCE-T" = "#F8766D", "Hydrogel control" = "#DB8E00", "Hydrogel HCE-T" = "#AEA200", "Tears" = "#64B200", "ALI hydrated" = "#00BD5C", "ALI dry" = "#00C1A7", "Shear stress" = "#00BADE", "Control" = "#00A6FF", "Reservoir" = "#B385FF", "Measurement medium" = "#EF67EB", "Artificial tears" = "#FF63B6")) +
  theme_prism(base_size = 28) +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())
```

## Statistics: Controls

Note: Due to the minimal variance in the No cells group compared to the Cells group, two separate ANOVAs were analysed instead of treating it as a single two-way nested ANOVA. This would have otherwise violated the homoscedasticity assumption and lead to an overestimation of significance for the pairwise comparisons within the Cells group as well as an underestimation of the significance for the pairwise comparisons within the No cells group.

Note: Levene's test reveals significant differences between group variances. Indeed, Hydrogel control standard deviation is 4.58 times the standard deviation of Reservoir. HC3 correction was preferred over GLS with varIdent as it is considered more robust.

Note: While a Type II ANOVA was chosen for practical reasons, the result would have been the same if Type I or Type III was chosen due to it being a one-way ANOVA.

```{r}

dat <- long[long$Group == "No cells",]
renamed_dat <- dat %>%
  rename(Fluorescence = `Fluorescence (RFU)`)

model <- lm(`Fluorescence (RFU)` ~ Condition, data = dat)
#model1 <- gls(Fluorescence ~ Condition, data = renamed_dat)
#model2 <- gls(Fluorescence ~ Condition, data = renamed_dat, weights = varIdent(form = ~1 | Condition))
#anova(model1, model2)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`Fluorescence (RFU)`",
         facet.by = "Condition",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Condition) %>%
  shapiro_test(Fluorescence)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`Fluorescence (RFU)` ~ Condition)
dat_summary <- dat %>%
  group_by(Condition) %>%
  get_summary_stats(`Fluorescence (RFU)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
#anova_results <- anova(model2)
print(anova_results)

## Pairwise
vcovHC3 <- vcovHC(model, type = "HC3")
emm_control <- emmeans(model, ~ Condition, vcov. = vcovHC3)
#emm_control <- emmeans(model2, ~ Condition, dat = renamed_dat, mode = "appx-satterthwaite")
pairs(emm_control, adjust = "bonferroni")
stat_control <- summary(pairs(emm_control, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_control_pos <- stat_control %>%
  add_xy_position(
    x = "Condition",
    data = dat,
    formula = `Fluorescence (RFU)` ~ Condition,
    step.increase = 0.36
  ) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Condition))),
    xmax = match(group2, levels(droplevels(dat$Condition))),
  )
```

## Visualisation: Controls

```{r}

dat <- droplevels(long[long$Group == "No cells",])
x <- dat$Condition
y <- dat$`Fluorescence (RFU)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  #geom_boxplot(width = 0.3, alpha = 0.2, outlier.shape = NA) +
  stat_summary(geom = "point", fun = "mean", size = 2, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(2700, 3400), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  stat_pvalue_manual(
    stat_control_pos,
    label = "p.adj.signif",
    size = 7.76,
    linewidth = 1
  ) +
  theme_prism(base_size = 28) +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())
```

## Normalisation

```{r}

normalised <- long %>%
  mutate( 
    `Normalised Fluorescence (AU)` = case_when(
      Condition == "Hydrogel HCE-T" ~ `Fluorescence (RFU)` / mean(`Fluorescence (RFU)`[Condition == "Hydrogel control"]),
      TRUE ~ `Fluorescence (RFU)` / mean(`Fluorescence (RFU)`[Condition == "Control"])
  )) %>%
  filter(Group != "No cells")
```

## Statistics: Cells

Note: Levene's test reveals significant differences between group variances. Indeed, ALI Dry standard deviation is 3.05 times the standard deviation of Apical AT.

```{r}

dat <- normalised
renamed_dat <- dat %>%
  rename(Fluorescence = `Fluorescence (RFU)`)

model <- lm(`Normalised Fluorescence (AU)` ~ Condition, data = dat)

## Normality
ggqqplot(data = residuals(model), 
         ggtheme = theme_prism()
         )
ggqqplot(data = dat,
         x = "`Normalised Fluorescence (AU)`",
         facet.by = "Condition",
         ggtheme = theme_prism()
         )

shapiro_test(residuals(model))
renamed_dat %>%
  group_by(Condition) %>%
  shapiro_test(Fluorescence)

## Homogeneity of variances
plot(model, 1)
dat %>% 
  levene_test(`Normalised Fluorescence (AU)` ~ Condition)
dat_summary <- dat %>%
  group_by(Condition) %>%
  get_summary_stats(`Fluorescence (RFU)`, type = "mean_sd")
max(dat_summary$sd)/min(dat_summary$sd)

## ANOVA
anova_results <- Anova(model, type = 2, white.adjust = "hc3")
print(anova_results)

## Pairwise
emm_options(parens = "a^")
vcovHC3 <- vcovHC(model, type = "HC3")
emm_cell <- emmeans(model, ~ Condition, vcov. = vcovHC3)
pairs(emm_cell, adjust = "bonferroni")
stat_cell <- summary(pairs(emm_cell, adjust = "bonferroni")) %>%
  separate(contrast, into = c("group1", "group2"),
           sep = " - ") %>%
  rename(p.adj = p.value) %>%
  add_significance("p.adj")
stat_cell_pos <- stat_cell %>%
  add_xy_position(
    x = "Condition",
    data = dat,
    formula = `Normalised Fluorescence (AU)` ~ Condition,
  ) %>%
  mutate(y.position = 15 + (row_number() * 1)) %>%
  mutate(
    xmin = match(group1, levels(droplevels(dat$Condition))),
    xmax = match(group2, levels(droplevels(dat$Condition))),
  )
```

## Visualisation: Cells

```{r}

dat <- normalised
x <- dat$Condition
y <- dat$`Normalised Fluorescence (AU)`

ggplot(data = dat, aes(x = x, y = y, color = Condition)) + 
  geom_violin(width = 0.5, scale = "width", alpha = 0.2, colour = "black", linewidth = 1) +
  geom_sina(size = 6, maxwidth = 0.5, scale = FALSE, alpha =
    0.4, stroke = 0) +
  stat_summary(geom = "point", fun = "mean", size = 0.5, shape = 3, colour = "black", stroke = 1.5) +
  stat_summary(geom = "errorbar", fun.data = "mean_sdl", fun.args = list(mult = 1), width = 0.2, colour = "black", linewidth = 1) +
  ylab(names(which(sapply(dat, identical, y = y)))) +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0), oob = oob_keep, guide = guide_prism_minor()) +
  coord_cartesian(clip = "off") +
  stat_pvalue_manual(
    stat_cell_pos,
    label = "p.adj.signif",
    tip.length = 0,
    size = 7.76,
    linewidth = 1,
  ) +
  geom_hline(yintercept = 1, linetype="dashed") +
  scale_color_manual(
    breaks = c("HCE-T", "Hydrogel control", "Hydrogel HCE-T", "Tears", "ALI hydrated", "ALI dry", "Shear stress", "Control", "Calibration resistor", "Measurement medium", "Artificial tears"),
    values = c("HCE-T" = "#F8766D", "Hydrogel control" = "#DB8E00", "Hydrogel HCE-T" = "#AEA200", "Tears" = "#64B200", "ALI hydrated" = "#00BD5C", "ALI dry" = "#00C1A7", "Shear stress" = "#00BADE", "Control" = "#00A6FF", "Calibration resistor" = "#B385FF", "Measurement medium" = "#EF67EB", "Artificial tears" = "#FF63B6")) +
  theme_prism(base_size = 28) +
  theme(plot.margin = margin(t = 50, b = 20, unit = "pt"), legend.key.spacing.y = unit(0.5, "lines"), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank())
```
